---
title: "Homework 6"
author: "LML"
date: "Nov 25 by 4:00pm"
output: github_document
---

Setup
```{r}
library(tidyverse)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
set.seed(1)
```

# Problem 1
```{r, load data}
child_data = 
  readr::read_csv("data/birthweight.csv") %>%
  janitor::clean_names() %>%
    mutate(
    gaweeks = fct_infreq(gaweeks)
    )

# quick overview
summary(child_data)
# check for missings
child_data[!complete.cases(child_data),]
```
```{r}
#initial model
fit = lm(bwt ~ gaweeks + ppwt, data = child_data) 
  #summary(fit)
  #summary(fit)$coef
  #coef(fit)
  #fitted.values(fit)
```

```{r}
modelr::add_residuals(nyc_airbnb, fit)
modelr::add_predictions(nyc_airbnb, fit)

nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = boro, y = resid)) + geom_violin()
```

Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.


# Problem 2
```{r, load data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
boot_straps = 
  sim_df_nonconst %>% 
  modelr::bootstrap(1000)
```

```{r}
sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```



