---
title: "Homework 6"
author: "LML"
date: "Nov 25 by 4:00pm"
output: github_document
---

Setup
```{r}
library(tidyverse)
library(modelr)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
set.seed(1)
```

# Problem 1

In the following chunck I load and tidy the dataset, creating factor variables for the categorical variables. I also quickly overview the data and check for missing data (there are none).
```{r, load data}
child_data = 
  readr::read_csv("data/birthweight.csv") %>%
  janitor::clean_names() %>%
    mutate(
    babysex = factor(babysex, labels = c("male", "female")),
    frace = factor(frace, levels = c(1, 2, 3, 4, 8, 9), labels = c("White", "Black", "Asian"," Puerto Rican", "Other", "Unknown")),
    malform = factor(malform, labels = c("absent", "present")),
    mrace = factor(mrace,  c(1, 2, 3, 4, 8, 9), labels = c("White", "Black", "Asian"," Puerto Rican", "Other", "Unknown"))
    )

# quick overview
summary(child_data)

# check for missings (no missings)
sum(complete.cases(child_data))
sum(!complete.cases(child_data))
```
For my model, I did a quick topical overview and chose the variables that seemed most influential in affecting a baby's birthweight.
```{r, my model}
#child_data %>% mutate(frace = fct_infreq(frace))

fit = lm(bwt ~ gaweeks + mrace + malform + pnumlbw + ppbmi, data = child_data) %>%
  broom::glance()
```

The following is a plot of residuals against fitted values from my model.
```{r, my plot residuals}
add_residuals(child_data, fit)
add_predictions(child_data, fit)

child_data %>% 
  add_residuals(fit) %>% 
  ggplot(aes(x = gaweeks, y = resid)) + geom_violin()
```

In the following chunk I build two models to compare to the model that I built.
```{r, comparison models}
# One using length at birth and gestational age as predictors (main effects only)
fit_compare_1 = lm(bwt ~ blength + gaweeks, data = child_data) %>%
  broom::glance()

#One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
fit_compare_2 = lm(bwt ~bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex + , data = child_data) %>%
  broom::glance()

```

The following chunk uses cross-validation to comparer the predictive performance of the three models.
```{r}
# fit my candidate models above and assess prediction accuracy
cv_child_data = 
  child_data %>% 
  mutate(fit  = map(train, ~lm(y ~ x, data = .x)),
         fit_compare_1  = map(train, ~mgcv::gam(y ~ s(x), data = .x)),
         fit_compare_2  = map(train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))) %>% 
  mutate(rmse_fit = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
         rmse_fit_compare_1 = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)),
         rmse_fit_compare_2 = map2_dbl(wiggly_mod, test, ~rmse(model = .x, data = .y)))

# plot below shows the distribution of RMSE values for each candidate model
cv_child_data %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()

```




# Problem 2

```{r, load data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
 simple linear regression with tmax as the response and tmin as the predictor
 distribution of two quantities estimated from these data:
r̂ 2
log(β̂ 0∗β̂ 1)
```{r}
boot_straps = 
  sim_df_nonconst %>% 
  modelr::bootstrap(1000)
```

```{r}
# Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words. 

sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```

Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂ 2 and log(β̂ 0∗β̂ 1). Note: broom::glance() is helpful for extracting r̂ 2 from a fitted regression, and broom::tidy() (with some additional wrangling) should help in computing log(β̂ 0∗β̂ 1)
```{r}

```


